### 2023-09-18 paper/app-faser.tex
revision completed

The same procedure applied to the FPF experiments in Sect.~\ref{sec:pdf4lhc21}
can also be used in the case of FASER$\nu$, for which pseudo-data is generated
for a Run III integrated
luminosity of $\mathcal{L}=150$ fb$^{-1}$.
%
As indicated by Table~\ref{tab:integrated_rates}, by the end of Run III, one expects
that FASER$\nu$ will have recorded around 300 and 900 electron- and muon-neutrinos
respectively corresponding to deep-inelastic scattering events, of which around 50
and 140 respectively are associated to charm-tagged events.
%
These projected event rates can be compared with the expectations for FASER$\nu$2, which predict
an increase in statistics of more than two orders of magnitude.

Fig.~\ref{fig:FASERnu2_vs_FASERnu} presents a similar comparison as that of
Fig.~\ref{fig:FASERnu2_baseline} now between the projected PDF impact of FASER$\nu$2 and that of
FASER$\nu$.
%
One finds that neutrino DIS measurements at FASER$\nu$ are unable to improve
PDF uncertainties as compared to the baseline scenario encapsulated by PDF4LHC21.
%
The reason is two-fold: the much smaller event rates as compared to FASER$\nu$2,
and the reduced coverage of the $(x,Q^2)$ phase space shown in Fig.~\ref{fig:fasernu2_muon}.
%
The differences in PDF sensitivity between FASER$\nu$ and FASER$\nu$2 in
Fig.~\ref{fig:FASERnu2_vs_FASERnu} illustrate
the  importance of realising the FPF in order to exploit the full physics potential enabled 
by LHC neutrinos for QCD and hadron structure studies.

>>>>

The same procedure applied to the FPF experiments in Sect.~\ref{sec:pdf4lhc21}
can also be used in the case of FASER$\nu$, for which pseudo-data is generated
for a Run III integrated
luminosity of $\mathcal{L}=150$ fb$^{-1}$.
%
As indicated by Table~\ref{tab:integrated_rates}, by the end of Run III, one expects
that FASER$\nu$ will have recorded around 600 and 1800 electron- and muon-neutrinos
respectively corresponding to deep-inelastic scattering events, of which around 100
and 300 respectively are associated to charm-tagged events.
%
These projected event rates can be compared with the expectations for FASER$\nu$2, which predict
an increase in statistics of more than two orders of magnitude.

Fig.~\ref{fig:FASERnu2_vs_FASERnu} presents a similar comparison as that of
Fig.~\ref{fig:FASERnu2_baseline} now between the projected PDF impact of FASER$\nu$2 and that of
FASER$\nu$.
%
One finds that neutrino DIS measurements at FASER$\nu$ are unable to improve
PDF uncertainties as compared to the baseline scenario encapsulated by PDF4LHC21.
%
The reason is two-fold: the smaller event rates as compared to FASER$\nu$2,
and the reduced coverage of the $(x,Q^2)$ phase space shown in Fig.~\ref{fig:fasernu2_muon}.
%
The differences in PDF sensitivity between FASER$\nu$ and FASER$\nu$2 in
Fig.~\ref{fig:FASERnu2_vs_FASERnu} illustrate
the  importance of realising the FPF in order to exploit the full physics potential enabled 
by LHC neutrinos for QCD and hadron structure studies.

### 2023-09-18 paper/app-nuclearPDFs.tex
revision completed

First of all, charm-tagged events are essential to achieve the best
sensitivity to the strange PDF, while they have a vanishing impact on the
other PDF combinations.
%
Second, not being able to identify the charge of the outgoing final-state lepton
does not markedly affect  the baseline results, with the possible exception
of the down valence quark PDF.
%
As discussed in Sect.~\ref{sec:nudis_revisited}, for a non-isoscalar target
such as tungsten, with $Z=74$ and $A-Z=110$, event rates with neutrino projectiles
will differ from those arising from antineutrino scattering, introducing
hence some additional information as compared to an isoscalar target in terms
of PDF sensitivity.

>>>>

First of all, charm-tagged events are essential to achieve the best
sensitivity to the strange PDF, while they have a vanishing impact on the
other PDF combinations.
%
Second, not being able to identify the charge of the outgoing final-state lepton
does not markedly affect  the baseline results, with the possible exception
of the down valence quark PDF.
%
As discussed in Sect.~\ref{sec:nudis_revisited}, for a non-isoscalar target
such as tungsten, with $Z=74$ and $A-Z=110$, event rates with neutrino projectiles
will differ from those arising from antineutrino scattering, introducing
additional information as compared to an isoscalar target in terms of PDF sensitivity.

### 2023-09-18 paper/sec-pheno.tex
revision completed

Fig.~\ref{fig:NNPDF40_pheno_integrated} displays
fiducial cross-section for representative LHC processes at $\sqrt{s}=14$ TeV
evaluated with NNPDF4.0 (top panels)
and with PDF4LHC21 (bottom panels),
compared with the results obtained from
the corresponding fits including the FPF structure function projections.
%
For the fits with FPF data we display the variants where the covariance matrix
consists only of statistical errors (``\_FPF'') and where also
systematic errors are accounted for (``\_FPF$^*$'').
%
For the baseline
predictions, the dark (light) bands indicate the 68\% (95\%) CL uncertainties.
%
The central values are set to be the same as in the baseline calculation in all cases.
%
From top to bottom, we show inclusive Drell-Yan production in the $Z$, $W^+$, and $W^-$
channels, Higgs production
in vector-boson fusion, Higgs associated
production, and diboson production in the $W^+W^-$, $W^+Z$, and $W^-Z$ final-states.
%
The corresponding comparisons at the level of differential distributions
are shown in Figs.~\ref{fig:NNPDF40_pheno_differential} and~\ref{fig:PDF4LHC21_pheno_differential}
for NNPDF4.0 and PDF4LHC21 respectively.
%
As done for the fiducial cross-sections of Fig.~\ref{fig:NNPDF40_pheno_integrated},
we only indicate the relative PDF uncertainty in each fit, with central values
assumed to be unchanged.

@@

@@

Inspection of Figs.~\ref{fig:NNPDF40_pheno_integrated}--\ref{fig:PDF4LHC21_pheno_differential}
confirms the potential of LHC neutrino structure function measurements
to improve theoretical predictions for Higgs, electroweak and high-mass
processes at the HL-LHC.
%
In general, qualitative consistency between the results based on NNPDF4.0
and on PDF4LHC21 is found, as was already the case at the PDF level.
%
As  compared to the limiting scenario where only statistical uncertainties
are taken into account, the reduction of PDF errors in the LHC cross-sections
obtained thanks for the FPF structure functions becomes less marked,
but still visible for most of the processes under consideration,
upon the inclusion of systematic uncertainties in the fit covariance matrix.

@@

In the case of the differential cross-sections displayed in Figs.~\ref{fig:NNPDF40_pheno_differential}
and~\ref{fig:PDF4LHC21_pheno_differential},
we observe how the impact of the FPF structure functions on LHC observables depends
on the hard-scattering scale.
%
For instance, searches for heavy resonances in the high-mass tail of the Drell-Yan
distributions could be improved by the addition of the FPF data.
%
Similar considerations apply for diboson prediction, and in the case of the $ZW^{\pm}$ channel we observe
an improvement specially in the low $p_{T,\ell\bar{\ell}}$ region which
represents the bulk of the fiducial cross-sections.
%
For the Higgs production processes, the PDF uncertainty in the theory predictions is relatively
stable as a function of the rapidity.
%
The effects of accounting for systematic uncertainties in the fit covariance
matrix are somewhat more visible here as compared to the inclusive cross-sections,
indicating that they affect mostly
the tails, rather than the bulk, of the distributions, and in particular the large-$x$
behaviour of the PDFs.
%
This observation emphasizes the importance of reducing systematic errors
in the FPF measurements in order to enhance the cross-talk with HL-LHC analyses.

>>>>

@@

Fig.~\ref{fig:NNPDF40_pheno_integrated} displays
fiducial cross-section for representative LHC processes at $\sqrt{s}=14$ TeV
evaluated with NNPDF4.0 (top panels)
and with PDF4LHC21 (bottom panels),
compared with the results obtained from
the corresponding fits including the FPF structure function projections.
%
For the fits with FPF data we display the variants where the covariance matrix
consists only of statistical errors (``\_FPF'') and where also
systematic errors are accounted for (``\_FPF$^*$'').
%
For the baseline
predictions, the dark (light) bands indicate the 68\% (95\%) CL uncertainties.
%
The central values are set to be the same as in the baseline calculation in all cases.
%
From top to bottom, we show inclusive Drell-Yan production in the $Z$, $W^+$, and $W^-$
channels, Higgs production
in vector-boson fusion, Higgs associated
production, and diboson production in the $W^+W^-$, $W^+Z$, and $W^-Z$ final-states.
%
The corresponding comparisons at the level of differential distributions
are shown in Figs.~\ref{fig:NNPDF40_pheno_differential} and~\ref{fig:PDF4LHC21_pheno_differential}
for NNPDF4.0 and PDF4LHC21 respectively.
%
As done for the fiducial cross-sections of Fig.~\ref{fig:NNPDF40_pheno_integrated},
we only indicate the relative PDF uncertainty in each fit.

@@

Inspection of Figs.~\ref{fig:NNPDF40_pheno_integrated}--\ref{fig:PDF4LHC21_pheno_differential}
confirms the potential of LHC neutrino structure function measurements
to improve theoretical predictions for Higgs, electroweak and high-mass
processes at the HL-LHC.
%
In general, qualitative consistency between the results based on NNPDF4.0
and on PDF4LHC21 is found, as was already the case at the PDF level.
%
As  compared to the best-case scenario where only statistical uncertainties
are taken into account, the reduction of PDF errors in the LHC cross-sections
obtained thanks for the FPF structure functions becomes less marked,
but still visible for most of the processes under consideration,
upon the inclusion of systematic uncertainties in the fit covariance matrix.

@@

In the case of the differential cross-sections displayed in Figs.~\ref{fig:NNPDF40_pheno_differential}
and~\ref{fig:PDF4LHC21_pheno_differential},
one observes
how the impact of the FPF structure functions on LHC observables depends
on the hard-scattering scale.
%
For instance, searches for heavy resonances in the high-mass tail of the Drell-Yan
distributions could be improved by the addition of the FPF data.
%
Similar considerations apply for diboson prediction, and in the case of the $ZW^{\pm}$ channel we observe
an improvement specially in the low $p_{T,\ell\bar{\ell}}$ region which
represents the bulk of the fiducial cross-sections.
%
For the Higgs production processes, the PDF uncertainty in the theory predictions is relatively
stable as a function of the rapidity.
%
The effects of accounting for systematic uncertainties in the fit covariance
matrix are somewhat more visible here as compared to the inclusive cross-sections,
indicating that they affect mostly
the tails, rather than the bulk, of the distributions, and in particular the large-$x$
behaviour of the PDFs.
%
This observation emphasizes the importance of reducing systematic errors
in the FPF measurements in order to enhance the cross-talk with HL-LHC analyses.
